---
title: "Deploying to a Server / the Cloud"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Deploying to a Server / the Cloud}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

As the interactive app has been built using [shiny](https://shiny.rstudio.com), there are several ways of deploying it. Two of the most common ways are explained in this document and additional information on deploying a shiny application can be found [here](https://shiny.rstudio.com/deploy/).

# Using shiny-server ✨

[Shiny-server](https://posit.co/products/open-source/shinyserver/) is an application to easily run shiny apps on a server.

Once you have a running instance of shiny-server, you can easily setup the interactive occupationMeasurement shiny app by adding a new script called `app.R` with the following code:

```{r eval=FALSE}
library(occupationMeasurement)

app()
```

You can of course carry over all the settings / your custom questionnaire passed to `app()` for a more complex configuration.

# Using docker 🐳

For easy deployment of the api, the package comes with a pre-built [docker](https://www.docker.com/) image called [`ghcr.io/occupationmeasurement/app:latest `](https://github.com/orgs/occupationMeasurement/packages/container/package/app).

To test this image on your local machine you can run the following command in your command line (this assumses you have Docker installed):

```bash
docker run --rm -p 3838:3838 -v $(pwd)/output:/srv/shiny-server/output ghcr.io/occupationmeasurement/app:latest
```

For more detailed information on the docker images if you e.g. want to build your own refer to the [docker directory](https://github.com/occupationMeasurement/occupationMeasurement/tree/main/docker) in the repository.
