---
title: "Deploying to a Server / the Cloud"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Deploying to a Server / the Cloud}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Deploying the Interactive Shiny App

As the interactive app has been built using [shiny](https://shiny.rstudio.com), there are several ways of deploying it. Two of the most common ways are explained in this document and additional information on deploying a shiny application can be found [here](https://shiny.rstudio.com/deploy/).

## Using shiny-server ✨

[Shiny-server](https://www.rstudio.com/products/shiny/shiny-server/) is an application to easily run shiny apps on a server.

Once you have a running instance of shiny-server, you can easily setup the interactive occupationMeasurement shiny app by adding a new script called `app.R` with the following code:

```{r eval=FALSE}
library(occupationMeasurement)

app()
```

You can of course carry over all the settings / your custom questionnaire passed to `app()` for a more complex configuration.

## Using docker 🐳

For easy deployment of the api, the package comes with a pre-built docker image called `occupation_measurement/api`.

To test this image on your local machine you can run the following command in your command line (this assumses you have Docker installed):

```bash
docker run --rm -p 3838:3838 -v $(pwd)/output:/srv/shiny-server/output occupation_measurement/app
```

For more detailed information on the docker images if you e.g. want to build your own refer to the [docker directory](https://github.com/occupationMeasurement/occupationMeasurement/tree/main/docker) in the repository.

# Deploying the API

The API comes with a pre-built Docker image for easy deployment on a server, your own computer or the cloud. If you wish to deploy the API without using docker, information on how to deploy a [plumber](https://www.rplumber.io) API can be found [here](https://www.rplumber.io/articles/hosting.html).

> Note that the `api()` function, will by default immediately start the API instead of returning a plumber instance. If you want to have access to the plumber instance for additional control during deployment, you can get it by calling the API via `api(start = FALSE)`.

## Using Docker 🐳

For easy deployment of the app, the package comes with a pre-built docker image called `occupation_measurement/app`.

To test this image on your local machine you can run the following command in your command line (this assumses you have Docker installed):

```bash
# Start the api
# it can be reached at http://localhost:8000
# Swagger documentation can be viewed at http://localhost:8000/__docs__/
```

For more detailed information on the docker images if you e.g. want to build your own refer to the [docker directory](https://github.com/occupationMeasurement/occupationMeasurement/tree/main/docker) in the repository.
