---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Interactive App

The classical way of using this package is by using the interactive shiny app that comes packaged with it. This app comes with "batteries-included" to run right out-of-the box and allow you to collect data immediately.

```{r eval=FALSE}
# Run the interactive shiny app
occupationMeasurement::app()
```

## Different Questionnaires

You're of course also not limited to using the app only with its default questionnaire. Indeed you can use any one of the ready-built questionnaires that come with the app, such as `questionnaire_web_survey()` (the default),`questionnaire_demo()` (to learn about the workings of the tool) or `questionnaire_guided_interview()` (for guided interviews with a professional interviewer).

```{r eval=FALSE}
library(occupationMeasurement)

app(
  # Learn more about the workings of the app with the demo questionnaire
  questionnaire = questionnaire_demo()
)
```

Moreover, you're also able to modify these questionnaires or just build your own, read more about this in `vignette("questionnaire")`.

## App Settings

There are also multiple settings available to the app to change how it behaves, where data is saved and much more. You can read about all options in `create_app_settings()`. If you're specifically looking to save data into a database, you can find a detailed explanation in `vignette("database")`.

```{r eval=FALSE}
library(occupationMeasurement)

app(
  # Use the questionnaire for guided interviews
  questionnaire = questionnaire_guided_interview(),
  app_settings = create_app_settings(
    # ... specify your custom settings here
    require_id = TRUE
  )
)
```

If you want to deploy the shiny app to an actual server for use in a production environment you can find the instructions in `vignette("deployment")`.

# JSON-API

If you're looking to integrate the package into your existing setup or tool the JSON-API that comes with the package might suit you better than the shiny app, due to it's increased flexibility. For more information on the api you can read `vignette("api")`.

## Starting the API

Starting the API is simple, as you will only need to call the `api()` method. This will immediately start a local plumber server and will open a window with the API's documentation.

```{r eval=FALSE}
# Start the API (and open its documentation)
occupationMeasurement::api()
```

## Usage

The API is designed to allow for similar usage as the interactive application, but implementing the UI and its logic has to be done manually. It is recommended to use the same text prompts as the shiny application for consistency.

The typical workflow for using the API is as follows:

1. Obtain a freetext response from the participant describing their occupation and its tasks.
2. Send this freetext response to `/v1/suggestions` to get a list of suggested categories.
3. Present this list to the participant for them choose an option. (There should always be the option of indicating that none of the suggested categories fit.)
4. Use the id of the chosen category to retrieve a list of possible followup questions `/v1/followup_questions` and present these to the user.
5. Use the code from the picked suggested category alongside the responses to the followup questions to get the final occupation category codes from `/v1/final_codes`.

Each of the API endpoints comes with a set of options / parameters which are described in the API's documentation. The API documentation is automatically available when starting the API, comes with the option to test out endpoints and provides example code on how to query the API.

# Included R-Functions

The package also exports some high-level functions to allow you to generate your own suggestions and work with them.

The functions are closely related to the API, so reading the above section on using the API may be helpful for a higher-level understanding of their relationship to each other.

The most interesting functions for external usage will be `get_job_suggestions()`, `get_followup_questions()` and `get_final_codes()`.
