---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package implements a toolbox of functionality to help with the (interactive) coding of occupations.

This includes (among other things) functionality to generate a list of suggestions for occupation categories based on free text input, to conduct a flexible interactive survey, to automatically save survey data in different forms and to make data and suggestions available via an API.

Occupation coding is currently mainly implemented by using the [German Auxiliary Classification of Occupations (AuxCO)](https://github.com/occupationMeasurement/auxiliary-classification) as it was specifically developed for interview settings. Final occupation codings are available for the International Standard Classification of Occupations 2008 (ISCO-08) and the German Klassifikation der Berufe 2010 (KldB-2010).

Due to limitations in available training data the tool is currently only implemented in German. Support for other languages, especially English, is planned, but pending on additional data. 

# Interactive App

The classical way of using this package is by using the interactive application that comes packaged with it. This app comes with "batteries-included" to run right out-of-the box and allow you to collect data immediately.

Detailed information on using the app, can be found in `vignette("app")` and the help page `?app`.

```{r eval=FALSE}
# Run the interactive shiny app
occupationMeasurement::app()
```

## Different Questionnaires

You're of course also not limited to using the app only with its default questionnaire. Indeed you can use any one of the ready-built questionnaires that come with the app, such as `questionnaire_web_survey()` (the default),`questionnaire_demo()` (to learn about the workings of the tool) or `questionnaire_interviewer_administered()` (for guided interviews with a professional interviewer).

```{r eval=FALSE}
library(occupationMeasurement)

app(
  # Learn more about the workings of the app with the demo questionnaire
  questionnaire = questionnaire_demo()
)
```

Moreover, you're also able to modify questionnaires or just build your own from scratch. You can read more about this functionality in `vignette("app-questionnaire")`.

Before you dive deeper into this technical software documentation, however, we strongly recommend you try the app with the `questionnaire_demo()` first.

# Alternative Usage

## JSON-API

If you're looking to integrate the package into your existing setup or tool the JSON-API that comes with the package might suit you better than the shiny app, due to it's increased flexibility. For more information on the api you can read `vignette("api")` and the help page `?api`.

## Included R-Functions

The package also exports some high-level functions to allow you to generate your own suggestions and work with them.

The functions are closely related to the API, so reading the above section on using the API may be helpful for a higher-level understanding of their relationship to each other.

The most interesting functions for external usage will be `get_job_suggestions()`, `get_followup_questions()` and `get_final_codes()`.
