---
title: "Building your own Questionnaire"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Building your own Questionnaire}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Questionnaires

When using the interactive shiny app you can use one of the different available questionnaires to e.g. conduct a web survey (`questionnaire_web_survey()`) or collect data from guided (phone) interviews (`questionnaire_guided_interview()`).

To be as flexible as possible, you can also modify these existing questionnaires or just build your own one from scratch.

## Pages

All questionnaires are built on top of pages. New pages can be created using the function `new_page()` or some of the other, more complex page helper functions.

In general each page has a unique `page_id` to identify itself and follows a general principle of lifecycle functions. First, its `condition` will be run to check whether the page should be displayed at all. If this function returns `FALSE` the page will be skipped.

If the condition is `TRUE`, the page will be shown and next the `run_before` function will be run to prepare everything for the page, followed by `render` to generate the page's actual outputs.

When the user navigates aways from a page the code in `run_after` will be run to e.g. save the users input and save data. Then, the next page's `condition` will be checked and so on. For a more detailed description of the page parameters and lifecycle you can also check out the documentation entry for `new_page()`.

To find some useful pre-built pages or helper functions to easily generate commonly used pages check out all functions whose name starts with `page_` in the reference.

## Building your own Questionnaire

Once you're comfortable building your own pages, building your own questionnaire is trivial, as a questionnaire is merely a list of pages.

An example for a simple questionnaire would be:

```{r eval=FALSE}
library(occupationMeasurement)
library(shiny)

my_simple_questionnaire <- list(
  new_page(
    page_id = "test",
    render = function(...) {
      return(
        p("Hello!"),
        button_previous(),
        button_next()
      )
    }
  ),

  # Create a custom page to choose your favorite meal
  page_choose_one_option(
    page_id = "favourite_meal",
    question_text = "Please pick your favorite kind of meal.",
    list_of_options = list(
      1 = "Breakfast",
      2 = "Lunch",
      3 = "Dinner"
    )
  )
)

# Test the questionnaire in the app
# app(questionnaire = my_simple_questionnaire)
```

As the general goal of this package is the measurement of occupations, you will usually want to at least include the core set of pages:

```{r eval=FALSE}
list(
  # ... some of your pages before ...
  page_first_freetext(),
  page_second_freetext(),
  page_select_suggestion(),
  page_none_selected_freetext(),
  page_followup(1),
  page_followup(2)
  # ... some of your pages after ...
)
```

## Modifying an existing Questionnaire

Apart from creating a new questionnaire from scratch, it's also possible to take an existing questionnaire and modify it to suit your needs.

To do this you can modify the questionnaire itself, by adding, removing or overwriting pages into it (as the questionnaire is just a list, it can be modified just like one).

```{r}
library(occupationMeasurement)
library(shiny)

questionnaire <- questionnaire_web_survey()

# Remove the first page (welcome)
questionnaire[[1]] <- NULL

# Use c() to add a new alternative page at the start
questionnaire <- c(
  list(
    new_page(
      "my_welcome",
      render = function() {
        return(h1("Hello!"))
      }
    )
  ),
  questionnaire
)

# Test the questionnaire in the app
# app(questionnaire = questionnaire)
```

Alternatively it's also possible to modify pages themselves (albeit a bit more complicated). Under the hood, pages are essentially also powered by lists and therefore their parameters can just be overwritten e.g. removing a page's condition check can be done by overwriting it via `page$condition <- NULL`.

As a page's different parameters usually depend on each other it's much easier to accidentaly break something. Therefore it is in general a good practice to overwrite a page's function by just wrapping it, like the example below.

```{r}
library(occupationMeasurement)
library(shiny)

questionnaire <- questionnaire_web_survey()

# Add some text to page_select_suggestion
print(questionnaire[[4]]$page_id)

original_select_suggestion_render <- questionnaire[[4]]$render
questionnaire[[4]]$render <- function(...) {
  return(c(
    list(
      p("~ My custom text before ~")
    ),
    original_select_suggestion_render(...)
  ))
}

# Test the questionnaire in the app
# app(questionnaire = questionnaire)
```

